---
title: "SWORK 881 week02"
author: "Stephen Omotayo Ololade "
date: "02/02/2022"
output: html_document
---

# load libraries
```{r setup, include=FALSE}

```



# Data
```{r}
# load data
give_your_data_name_here<- read_csv("")
```


```{r}

Data.01 <- read_csv("Data/LHS_exercise_01272022.csv")

```



```{r}
install.packages("tidymodels",dependencies = T)
```


```{r}
#how many observations and variables? 
# 268 obsevations,  8 variables
``` 
#how many observations and variables? 
[provide your answer here]

# 268 obsevations,  8 variables

```{r}
# create a new variable called `depression` by summing all ptsd variables. Use tidy approach
# Additional one variable created
```
#let selects some variables

```{r}

data.02<- Data.01%>%
  mutate(depression = rowSums(across(ptsd1_1:ptsd4_1), na.rm=T)) 
        
```


```{r}
#run simple descriptive statistics for all variables
```

#let's do descriptive statistics

```{r}

summary(Data.01)


```

DESCRIBE THE DATA BRIEFLY HERE
[provide your answer here]



```{r}
##There are 9 variables consting of response identity, age, sex, education and four levels of depression scores.
##The age ranges between 18 and 70years with the mean=32 ()
```

# Model and Visualization
> What is the effect of `age`, `sex`, and `education` on `depression score`? 

Create a linear regression model that answers the question above. Print the results of the output and model diagnostics.


#lets create a summed variable called  depression score
```{r}
data.03<- Data.01%>%
  select(ptsd1_1, ptsd2_1, ptsd3_1, ptsd4_1, age, sex, education)%>%
  mutate(ptsd_score = rowSums(across(ptsd1_1:ptsd4_1), na.rm=T), 
         ptsd_mean = rowMeans(across(ptsd1_1:ptsd4_1), na.rm=T))


```

# Let's create
```{r}

fit.1 <- lm(ptsd_score ~ age,
            data = data.03)

summary(fit.1)

## Age is significantly associated with depression score . p-value: 0.003966
  # Adjusted R-squared:0.02713

### Education: p-value: 0.07;  djusted R-squared: 0.01173
# Sex :p-value: 0.1596;  djusted R-squared: 0.00368
## sex and education are not significantly associated with depression score 



```



```{r}
fit.1 <- lm(depression ~education, 
            data.03=data.02)


summary (fit.1)



```


```{r}
# model diagnostics


```


```{r}
# use ggplot to plot histogram of residuals (use 20 bins)
ggplot(fit.1, 
       aes(fit.1$residuals))+
  geom_histogram(bins=20)

```

```{r}
ggplot(fit.1, 
       aes(fit.1$residuals))+
  geom_histogram(bins=100)

```
``
```{r}


```
```{r}
par(mfrow =c(2,2))
plot (fit.1)

```

`{r}


```




# Discussion of Results

Describe and interpret your results, including any statistical information you believe important: 


```{r} The current study examines possible factors influecing the depression scales. Linear regression model indicated that sex is a significant factor that determines the depression scores of individual. Athough, it was not certain from the study what role that gender plays

```


```{re
#.
```

